Information Disclosure in Dynamic Innovation Contests

### 2025-04-23 paper/Paper.tex
update-paper

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $(\tilde{y}_t, t) \in\mathbb{R}\times[0, T)$ are given by
\begin{equation*}
\begin{aligned}
m_{i}(\tilde{y}_t, t) &= \frac{e^{-z_t^2/2}\sqrt{\lambda\bar{S}}}{2\sqrt{2\pi(T-t)}} \cdot \left[\gamma(\rho_{1}) + \gamma(\rho_{2})\right]\left[1-\rho(z_t)^2\right]\left[1 + \rho(z_t)\right]\\
m_{j}(\tilde{y}_t, t) &= \frac{e^{-z_t^2/2}\sqrt{\lambda\bar{S}}}{2\sqrt{2\pi(T-t)}} \cdot 
 \left[\gamma(\rho_{1}) + \gamma(\rho_{2})\right]\left[1-\rho(z_t)^2\right]\left[1 - \rho(z_t)\right]
\end{aligned}
\end{equation*}
where $z_t = \tilde{y}_t / \sqrt{\lambda\bar{S}(T-t)}$, $\rho(z_t) = \gamma^{-1}\left(\Phi(z_t)\left[\gamma(\rho_{1})+\gamma(\rho_{2})\right]-\gamma(\rho_{2})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},
\end{equation*}
\begin{equation*}
\rho_{1} = \frac{e^{w_{1}}+e^{-w_{2}}-2}{e^{w_{1}}-e^{-w_{2}}},
\quad
\rho_{2} = \frac{e^{w_{2}}+e^{-w_{1}}-2}{e^{w_{2}}-e^{-w_{1}}},
\quad
w_{i} = \frac{\theta}{\lambda\bar{S}c_i}. 
\end{equation*}
\end{lemma}

@@

\section{Structural Estimation}

>>>>

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $(\tilde{y}_t, t) \in\mathbb{R}\times[0, T)$ are given by
\begin{equation*}
m_{i}(\tilde{y}_t, t) = \frac{e^{-z_t^2/2}\lambda^{1/4}\sigma^{1/2}}{2\sqrt{2\pi(T-t)}} \cdot \left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z_t)^2\right]\left[1 + \rho(z_t)\right]
\end{equation*}
\begin{equation*}
m_{j}(\tilde{y}_t, t) = \frac{e^{-z_t^2/2}\lambda^{1/4}\sigma^{1/2}}{2\sqrt{2\pi(T-t)}} \cdot 
 \left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z_t)^2\right]\left[1 - \rho(z_t)\right]
\end{equation*}
where $z_t = \tilde{y}_t / \sqrt{\lambda^{1/2}\sigma(T-t)}$, $\rho(z_t) = \gamma^{-1}\left(\Phi(z_t)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\lambda^{1/2}\sigma c_{i(j)}}.
\end{equation*}
\end{lemma}

@@

\section{Model Estimation}

Unknown parameters to be estimated: 
\begin{itemize}
	\item $\sigma$ (Total innovation risk): 
	\item $\rho_i$ and $\rho_j$ (Capacities)
\end{itemize}

Likelihood: 
Data are submission times $\{t^i_k\}_{k=1}^{N_i}$ and $\{t^j_k\}_{k=1}^{N_i}$.

We assume the submission times follow inhomogeneous Poisson process, controlled by the effort functions $\tau_i(t)$ and $\tau_j(t)$. 
Then, during any time interval of the contest $\mathcal{S}$, the Poisson arrival rate of submissions of the representative player $i$ is given by $\int_{s\in\mathcal{S}}\tau_i(s)ds$. 
The likelihood function of any realization of this point process $\{t^i_k\}_{k=1}^{N_i}$ is given by 
\begin{equation*}
p\left(\{t^i_k\}_{k=1}^{N_i} | \tau_i\right) = \exp\left\{-\int_{s\in\mathcal{D}}\tau_i(s)ds\right\}\prod_{k=1}^{N_i}\tau_i(t^i_k)
\end{equation*}

\section{Application}

\subsection{Synthetic Data}

Before applying our estimation procedure to real-world contest data, we evaluate its potential on synthetically generated data.

\subsection{Case Study}

\newpage
\section{Conclusion}
